### 2020-06-19 introduction.tex
Some intro chapter edits

Since the Industrial Revolution in the 1800s, rapidly rising greenhouse gas
emissions have contributed significantly to global warming. The consequences
have been acutely felt in recent years through increasingly frequent
and record breaking extreme weather events. Urgent measures are necessary to
limit CO$_2$ emissions and the negative impacts of global warming.

Since electricity generation from burning fossil fuels represents the
largest source of CO$_2$ emissions (38\% in 2018 \cite{iea_global_2019}),
replacing them with low-carbon
alternatives would effectively curb a large fraction of emissions. Out
of all low-carbon power sources, nuclear power is arguably best suited to
replace fossil fuel burning; it provides consistent base-load
power independent of weather and local geographical conditions. Solar and wind
power are dependent on favorable weather conditions while hydropower requires
relatively more area and is limited to geologically appropriate locations.
This argument provides a strong case for nuclear power being the most
appropriate and realistic alternative to burning fossil fuels for our current
and future electricity needs.

Large-scale reactor deployments are necessary to displace the
presently large share of energy production from fossil fuel power plants.
However, several obstacles stand in the way of mass reactor deployments. These
include perceived safety risks, sustainability concerns, nuclear proliferation
risks, and the ability to compete economically with other sources of energy.
The \gls{MSR} concept, one of six advanced reactor designs
selected by the \gls{GIF} \cite{gif_technology_2002} for continued research
and development, is a potential solution to the aforementioned issues.

The primary coolant in MSRs is a molten salt mixture
with fissile and/or fertile material directly dissolved in the coolant.
MSRs possess an inherently robust safety feature in the
strongly negative fuel temperature reactivity coefficient from Doppler
broadening and thermal fuel expansion that greatly reduces
the risk of a reactor power excursion. Many designs can also incorporate the
thorium fuel cycle for improved sustainability arising from the use of
abundant natural thorium resources and reduced transuranic waste. The
resultant reduced radiotoxicity from transuranic waste also reduces costs
associated with long-term nuclear waste storage. In addition, the ability to
operate at near atmospheric pressures eliminates the need for a thick pressure
vessel and drives down construction costs, while online fuel reprocessing
reduces reactor downtime during reactor operation.

However, the liquid fuel form also brings about novel computational
challenges in simulating the transient behavior of \glspl{MSR}; the
neutronics and thermal-hydraulics are more tightly coupled due to the strong
temperature reactivity coefficient, and the additional advection coupling
terms. Furthermore, we have to account for the movement of \glspl{DNP} as
they are now generated directly within the primary coolant loop. Therefore,
the choice of coupling methods for each set of physics requires careful
consideration. Existing reactor system-level codes and modeling approaches
for conventional \gls{LWR} analysis contain reactor-specific assumptions in
multiphysics coupling and other areas that render the techniques less suitable
for simulating \glspl{MSR}. Thus, making minor modifications to these codes
without changing the underlying algorithms is not the best approach for
\gls{MSR} safety analysis.

>>>>

Greenhouse gas emission from human activities is the main cause of climate
change, a global phenomenon characterized by shifting weather patterns and
rising temperatures. Climate change has dire consequences on human health and
safety due to extreme weather events and the overall impact on food
production. As a result, urgent measures are necessary to limit greenhouse gas
emissions, namely CO$_2$ emissions from electricity generation.

Electricity generation from burning fossil fuels represents the
largest source of CO$_2$ emissions (38\% in 2018 \cite{iea_global_2019});
replacing it with low-carbon
alternatives would curb a large fraction of emissions. Nuclear power is
a viable low-carbon replacement for burning fossil fuels.
Other low-carbon energy sources include solar-, wind-, and hydro-power. Each
energy source has its own set of advantages and disadvantages; nuclear power's
advantage over renewable energy sources is that it provides consistent
base-load power independent of weather and geographical location (cite mit).
Employing a diverse mix of these energy sources ensures energy security and
reliability during and after our transition towards a low-carbon future (cite mit).

The world would have to ramp up the current rate of reactor deployments to
displace some of the
presently large share of energy production from fossil fuel power plants.
However, several obstacles stand in the way of mass reactor deployments. These
include perceived safety risks, sustainability concerns, nuclear proliferation
risks, and the ability to compete economically with other sources of energy.
A potential solution to the aforementioned issues is
the \gls{MSR} concept, one of six advanced reactor designs
selected by the \gls{GIF} \cite{gif_technology_2002} for continued research
and development.

The primary coolants in MSRs consist of a molten salt mixture
with fissile and/or fertile material directly dissolved in the coolant.
MSRs possess an inherently robust safety feature in the strongly negative fuel
temperature coefficient of reactivity. Some designs can also incorporate the
thorium fuel cycle for improved sustainability arising from the use of
abundant natural thorium resources and reduced transuranic waste. The
latter also reduces economical costs
associated with long-term nuclear waste storage. In addition, the ability to
operate at near atmospheric pressures eliminates the need for a thick pressure
vessel and drives down construction costs, while online fuel reprocessing
reduces reactor downtime during reactor operation.

However, the liquid fuel form also brings about novel computational
challenges in simulating the transient behavior of \glspl{MSR}; the
neutronics and thermal-hydraulics are tightly coupled due to the strong
temperature reactivity coefficient. Furthermore, we have to account for the
movement of \glspl{DNP} as
they are now generated directly within the primary coolant loop. Therefore,
the choice of coupling methods for each set of physics requires careful
consideration. Existing reactor system-level software and modeling approaches
for conventional \gls{LWR} analysis contain reactor-specific assumptions in
multiphysics coupling and other areas that render the techniques less suitable
for simulating \glspl{MSR}. Thus, making minor modifications to these codes
without changing the underlying algorithms is not the best approach for
\gls{MSR} safety analysis.
